---
title: "Protobuf in REST Applications Analysis"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

# Analysis

# Baseline

**Conditions**

Test Setup

\|- Baseline Thread Group\
\|-\|-- GET All Plan\
\|-\|-- GET Plan from User\
\|-\|-- POST Create Subscriber\
\|-\|-- POST Create Plan

Thread Options

| Number of Threads | Ramp-up period (s) | Loop Count | Duration (s) |
|-------------------|--------------------|------------|--------------|
| 10                | 5                  | Infinite   | 180          |

```{r}
library(readr)

## Global Stats

stats <- read_csv("../Stats.csv")

## Load JSON files

jGP <- read_csv("../baseline/json_get_plan_data.csv")

jGSP <- read_csv("../baseline/json_get_specific_plan_data.csv")

jPCP <- read_csv("../baseline/json_post_plan_data.csv")

jPCS <- read_csv("../baseline/json_post_subs_data.csv")


## Load Protocol Buffers files

pGP <- read_csv("../baseline/protobuf_get_plan_data.csv")

pGSP <- read_csv("../baseline/protobuf_get_specific_plan_data.csv")

pPCP <- read_csv("../baseline/protobuf_post_plan_data.csv")

pPCS <- read_csv("../baseline/protobuf_post_subs_data.csv")



#### MEAN

## MEAN Elapsed

# JSON

mTimeJGP<-mean(jGP$elapsed)
mTimeJGSP<-mean(jGSP$elapsed)
mTimeJPCP<-mean(jPCP$elapsed)
mTimeJPCS<-mean(jPCS$elapsed)


# Protobuf

mTimePGP<-mean(pGP$elapsed)
mTimePGSP<-mean(pGSP$elapsed)
mTimePPCP<-mean(pPCP$elapsed)
mTimePPCS<-mean(pPCS$elapsed)

## MEAN Bytes

# JSON

mBytesJGP<-mean(jGP$bytes)
mBytesJGSP<-mean(jGSP$bytes)
mBytesJPCP<-mean(jPCP$bytes)
mBytesJPCS<-mean(jPCS$bytes)


# Protobuf

mBytesPGP<-mean(pGP$bytes)
mBytesPGSP<-mean(pGSP$bytes)
mBytesPPCP<-mean(pPCP$bytes)
mBytesPPCS<-mean(pPCS$bytes)

```

## Bar Plot

### Endpoint - GET Plan

#### Elapsed Time

```{r}
title <- "Baseline GET Plan Elapsed Time"
data <- round(c(mTimePGP, mTimeJGP),2)
names <- c("Protobuf", "JSON")
axis <- c("Data Format","Elapsed Time (ms)")
bar_colors <- c("plum2", "cyan3")
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")
legend("topright", legend = names, fill = bar_colors)

```

#### Bytes

```{r}
title <- "Baseline GET Plan Bytes"
data <- round(c(mBytesPGP, mBytesJGP), 2)
names <- c("Protobuf", "JSON")
axis <- c("Data Format","Bytes")
bar_colors <- c("plum2", "cyan3")
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")
legend("topright", legend = names, fill = bar_colors)
```

#### Throughput

```{r}
title <- "Baseline GET Plan Throughput"
data <- c(stats$Throughput[1],stats$Throughput[13])
names <- c("Protobuf", "JSON")
axis <- c("Data Format","Throughput /sec ")
bar_colors <- c("plum2", "cyan3")
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")
legend("topright", legend = names, fill = bar_colors)
```

### Endpoint - GET Specific Plan

#### Elapsed Time

```{r}
title <- "Baseline GET Specific Plan Elapsed Time"
data <- round(c(mTimePGSP, mTimeJGSP),2)
names <- c("Protobuf", "JSON")
axis <- c("Data Format","Elapsed Time (ms)")
bar_colors <- c("plum2", "cyan3")
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")
legend("topright", legend = names, fill = bar_colors)
```

#### Bytes

```{r}
title <- "Baseline GET Specific Plan Bytes"
data <- round(c(mBytesPGSP, mBytesJGSP), 2)
names <- c("Protobuf", "JSON")
axis <- c("Data Format","Bytes")
bar_colors <- c("plum2", "cyan3")
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")
legend("topright", legend = names, fill = bar_colors)
```

#### Throughput

```{r}
title <- "Baseline GET Specific Plan Throughput"
data <- c(stats$Throughput[2],stats$Throughput[14])
names <- c("Protobuf", "JSON")
axis <- c("Data Format","Throughput /sec ")
bar_colors <- c("plum2", "cyan3")
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")
legend("topright", legend = names, fill = bar_colors)


```

### Endpoint - POST Subscriber

#### Elapsed Time

```{r}
title <- "Baseline POST Subscriber Elapsed Time"
data <- round(c(mTimePPCS, mTimeJPCS),2)
names <- c("Protobuf", "JSON")
axis <- c("Data Format","Elapsed Time (ms)")
bar_colors <- c("plum2", "cyan3")
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")
legend("topright", legend = names, fill = bar_colors)


```

#### Bytes

```{r}
title <- "Baseline POST Subscriber Bytes"
data <- round(c(mBytesPPCS, mBytesJPCS), 2)
names <- c("Protobuf", "JSON")
axis <- c("Data Format","Bytes")
bar_colors <- c("plum2", "cyan3")
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")
legend("topright", legend = names, fill = bar_colors)

```

#### Throughput

```{r}
title <- "Baseline POST Subscriber Throughput"
data <- c(stats$Throughput[3],stats$Throughput[15])
names <- c("Protobuf", "JSON")
axis <- c("Data Format","Throughput /sec ")
bar_colors <- c("plum2", "cyan3")
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")
legend("topright", legend = names, fill = bar_colors)

```

### Endpoint - POST Plan

#### Elapsed Time

```{r}
title <- "Baseline POST Plan Elapsed Time"
data <- round(c(mTimePPCP, mTimeJPCP), 2)
names <- c("Protobuf", "JSON")
axis <- c("Data Format", "Elapsed Time (ms)")
bar_colors <- c("plum2", "cyan3")
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title, ylim = c(0, max(data) + max(data)/3))
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")
legend("topright", legend = names, fill = bar_colors)


```

#### Bytes

```{r}
title <- "Baseline POST Plan Bytes"
data <- round(c(mBytesPPCP, mBytesJPCP), 2)
names <- c("Protobuf", "JSON")
axis <- c("Data Format","Bytes")
bar_colors <- c("plum2", "cyan3")
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")
legend("topright", legend = names, fill = bar_colors)

```

#### Throughput

```{r}
title <- "Baseline POST Plan Throughput"
data <- c(stats$Throughput[4],stats$Throughput[16])
names <- c("Protobuf", "JSON")
axis <- c("Data Format","Throughput /sec ")
bar_colors <- c("plum2", "cyan3")
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")
legend("topright", legend = names, fill = bar_colors)

```
# Load

**Conditions**

Test Setup

\|- Baseline Thread Group\
\|-\|-- GET All Plan\
\|-\|-- GET Plan from User\
\|-\|-- POST Create Subscriber\
\|-\|-- POST Create Plan

Thread Options

| Number of Threads | Ramp-up period (s) | Loop Count | Duration (s) |
|-------------------|--------------------|------------|--------------|
| 600                | 30                  | Infinite   | 360          |


```{r}
library(readr)

## Global Stats

stats <- read_csv("../Stats.csv")

## Load JSON files

jGP <- read_csv("../load/json_get_plan_data.csv")


jGSP <- read_csv("../load/json_get_specific_plan_data.csv")



jPCP <- read_csv("../load/json_post_plan_data.csv")


jPCS <- read_csv("../load/json_post_subs_data.csv")


## Load Protocol Buffers files

pGP <- read_csv("../load/protobuf_get_plan_data.csv")


pGSP <- read_csv("../load/protobuf_get_specific_plan_data.csv")



pPCP <- read_csv("../load/protobuf_post_plan_data.csv")


pPCS <- read_csv("../load/protobuf_post_subs_data.csv")



#### MEAN

## MEAN Elapsed

# JSON

mTimeJGP<-mean(jGP$elapsed)
mTimeJGSP<-mean(jGSP$elapsed)
mTimeJPCP<-mean(jPCP$elapsed)
mTimeJPCS<-mean(jPCS$elapsed)


# Protobuf

mTimePGP<-mean(pGP$elapsed)
mTimePGSP<-mean(pGSP$elapsed)
mTimePPCP<-mean(pPCP$elapsed)
mTimePPCS<-mean(pPCS$elapsed)

## MEAN Bytes

# JSON

mBytesJGP<-mean(jGP$bytes)
mBytesJGSP<-mean(jGSP$bytes)
mBytesJPCP<-mean(jPCP$bytes)
mBytesJPCS<-mean(jPCS$bytes)


# Protobuf

mBytesPGP<-mean(pGP$bytes)
mBytesPGSP<-mean(pGSP$bytes)
mBytesPPCP<-mean(pPCP$bytes)
mBytesPPCS<-mean(pPCS$bytes)

```

## Bar Plot

### Endpoint - GET Plan

#### Elapsed Time
```{r}
title <- "Load GET Plan Elapsed Time"
data <- round(c(mTimePGP, mTimeJGP),2)
names <- c("Protobuf", "JSON")
axis <- c("Data Format","Elapsed Time (ms)")
bar_colors <- c("plum2", "cyan3")
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")
legend("topright", legend = names, fill = bar_colors)

```

#### Bytes
```{r}
data <- round(c(mBytesPGP, mBytesJGP), 2)
names <- c("Protobuf", "JSON")
axis <- c("Data Format","Bytes")
bar_colors <- c("plum2", "cyan3")
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")
legend("topright", legend = names, fill = bar_colors)
```

#### Throughput
```{r}
title <- "Load GET Plan Throughput"
data <- c(stats$Throughput[5],stats$Throughput[17])
names <- c("Protobuf", "JSON")
axis <- c("Data Format","Throughput /sec ")
bar_colors <- c("plum2", "cyan3")
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")

legend("topright", legend = names, fill = bar_colors)

```

### Endpoint - GET Specific Plan

#### Elapsed Time
```{r}
title <- "Load GET Specific Plan Elapsed Time"
data <- round(c(mTimePGSP, mTimeJGSP),2)
names <- c("Protobuf", "JSON")
axis <- c("Data Format","Elapsed Time (ms)")
bar_colors <- c("plum2", "cyan3")
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")
legend("topright", legend = names, fill = bar_colors)
```

#### Bytes
```{r}
title <- "Load GET Specific Plan Bytes"
data <- round(c(mBytesPGSP, mBytesJGSP), 2)
names <- c("Protobuf", "JSON")
axis <- c("Data Format","Bytes")
bar_colors <- c("plum2", "cyan3")
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")
legend("topright", legend = names, fill = bar_colors)
```

#### Throughput
```{r}
title <- "Load GET Specific Plan Throughput"
data <- c(stats$Throughput[6],stats$Throughput[18])
names <- c("Protobuf", "JSON")
axis <- c("Data Format","Throughput /sec ")
bar_colors <- c("plum2", "cyan3")
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")
legend("topright", legend = names, fill = bar_colors)
```

#### Error
```{r}
title <- "Load GET Specific Plan Error"
data <- c(stats$Error[6],stats$Error[18])
names <- c("Protobuf", "JSON")
axis <- c("Data Format","Error %")
bar_colors <- c("plum2", "cyan3")
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))
text(x = graph, y = data, labels = data, pos = 3, col = "black")
legend("topright", legend = names, fill = bar_colors)
```

### Endpoint - POST Subscriber

#### Elapsed Time
```{r}
title <- "Load POST Subscriber Elapsed Time"
data <- round(c(mTimePPCS, mTimeJPCS),2)
names <- c("Protobuf", "JSON")
axis <- c("Data Format","Elapsed Time (ms)")
bar_colors <- c("plum2", "cyan3")
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")
legend("topright", legend = names, fill = bar_colors)
```

#### Bytes
```{r}
title <- "Load POST Subscriber Bytes"
data <- round(c(mBytesPPCS, mBytesJPCS), 2)
names <- c("Protobuf", "JSON")
axis <- c("Data Format","Bytes")
bar_colors <- c("plum2", "cyan3")
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")
legend("topright", legend = names, fill = bar_colors)

```

#### Throughput
```{r}
title <- "Load POST Subscriber Throughput"
data <- c(stats$Throughput[7],stats$Throughput[19])
names <- c("Protobuf", "JSON")
axis <- c("Data Format","Throughput /sec ")
bar_colors <- c("plum2", "cyan3")
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")
legend("topright", legend = names, fill = bar_colors)
```

#### Error

```{r}
title <- "Load POST Subscriber Error"
data <- c(stats$Error[7],stats$Error[19])
names <- c("Protobuf", "JSON")
axis <- c("Data Format","Error %")
bar_colors <- c("plum2", "cyan3")
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))
text(x = graph, y = data, labels = data, pos = 3, col = "black")
legend("topright", legend = names, fill = bar_colors)
```


### Endpoint - POST Plan

#### Elapsed Time

```{r}
title <- "Load POST Plan Elapsed Time"
data <- round(c(mTimePPCP, mTimeJPCP),2)
names <- c("Protobuf", "JSON")
axis <- c("Data Format","Elapsed Time (ms)")
bar_colors <- c("plum2", "cyan3")
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")
legend("topright", legend = names, fill = bar_colors)
```


#### Bytes
```{r}
title <- "Load POST Plan Bytes"
data <- round(c(mBytesPPCP, mBytesJPCP), 2)
names <- c("Protobuf", "JSON")
axis <- c("Data Format","Bytes")
bar_colors <- c("plum2", "cyan3")
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")
legend("topright", legend = names, fill = bar_colors)
```

#### Throughput
```{r}
title <- "Load POST Plan Throughput"
data <- c(stats$Throughput[8],stats$Throughput[20])
names <- c("Protobuf", "JSON")
axis <- c("Data Format","Throughput /sec ")
bar_colors <- c("plum2", "cyan3")
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")
legend("topright", legend = names, fill = bar_colors)

```
# Stress

**Conditions**

Test Setup

\|- Baseline Thread Group\
\|-\|-- GET All Plan\
\|-\|-- GET Plan from User\
\|-\|-- POST Create Subscriber\
\|-\|-- POST Create Plan

Thread Options

| Number of Threads | Ramp-up period (s) | Loop Count | Duration (s) |
|-------------------|--------------------|------------|--------------|
| 3000                | 100             | Infinite   | 600          |

```{r}
library(readr)

## Global Stats

stats <- read_csv("../Stats.csv")

## Stress JSON files

jGP <- read_csv("../stress/json_get_plan_data.csv")
jGSP <- read_csv("../stress/json_get_specific_plan_data.csv")
jPCP <- read_csv("../stress/json_post_plan_data.csv")
jPCS <- read_csv("../stress/json_post_subs_data.csv")

## Stress Protocol Buffers files

pGP <- read_csv("../stress/protobuf_get_plan_data.csv")
pGSP <- read_csv("../stress/protobuf_get_specific_plan_data.csv")
pPCP <- read_csv("../stress/protobuf_post_plan_data.csv")
pPCS <- read_csv("../stress/protobuf_post_subs_data.csv")


#### MEAN

## MEAN Elapsed

# JSON

mTimeJGP<-mean(jGP$elapsed)
mTimeJGSP<-mean(jGSP$elapsed)
mTimeJPCP<-mean(jPCP$elapsed)
mTimeJPCS<-mean(jPCS$elapsed)

# Protobuf

mTimePGP<-mean(pGP$elapsed)
mTimePGSP<-mean(pGSP$elapsed)
mTimePPCP<-mean(pPCP$elapsed)
mTimePPCS<-mean(pPCS$elapsed)

## MEAN Bytes

# JSON

mBytesJGP<-mean(jGP$bytes)
mBytesJGSP<-mean(jGSP$bytes)
mBytesJPCP<-mean(jPCP$bytes)
mBytesJPCS<-mean(jPCS$bytes)


# Protobuf

mBytesPGP<-mean(pGP$bytes)
mBytesPGSP<-mean(pGSP$bytes)
mBytesPPCP<-mean(pPCP$bytes)
mBytesPPCS<-mean(pPCS$bytes)

```

## Bar Plot

### Endpoint - GET Plan

#### Elapsed Time
```{r}
title <- "Stress GET Plan Elapsed Time"

# Graph Data

data <- round(c(mTimePGP, mTimeJGP),2)

# Bar Names Labels
names <- c("Protobuf", "JSON")

# Bar Axis Names

axis <- c("Data Format","Elapsed Time (ms)")

# Custom colors for the bars
bar_colors <- c("plum2", "cyan3")

# Create Bar
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))
# Calculate median values
medians <- c(median(pGP$elapsed),median(jGP$elapsed))

for (i in 1:length(medians)) {
  # Add a line for the current median value
  lines(x = c(graph[i] - 0.4, graph[i] + 0.4), y = c(medians[i], medians[i]), col = "black", lwd = 2)
  
  # Add text label for the current median value
  text(x = graph[i], y = medians[i] + 1, labels = medians[i], pos = 3, col = "black")
}
# Add Value For Each Bar
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")

# Graph Color Legend
legend("topright", legend = names, fill = bar_colors)

```

#### Bytes
```{r}
title <- "Stress GET Plan Bytes"

# Graph Data
data <- round(c(mBytesPGP, mBytesJGP), 2)

# Bar Names Labels
names <- c("Protobuf", "JSON")

# Bar Axis Names

axis <- c("Data Format","Bytes")

# Custom colors for the bars
bar_colors <- c("plum2", "cyan3")

# Create Bar
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))

# Add Value For Each Bar
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")

# Graph Color Legend
legend("topright", legend = names, fill = bar_colors)
```

#### Throughput
```{r}
# Graph Title

title <- "Stress GET Plan Throughput"

# Graph Data
data <- c(stats$Throughput[9],stats$Throughput[21])

# Bar Names Labels
names <- c("Protobuf", "JSON")

# Bar Axis Names

axis <- c("Data Format","Throughput /sec ")

# Custom colors for the bars
bar_colors <- c("plum2", "cyan3")

# Create Bar
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))

# Add Value For Each Bar
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")

# Graph Color Legend
legend("topright", legend = names, fill = bar_colors)
```

#### Error
```{r}
# Graph Title

title <- "Stress GET Plan Error"

# Graph Data
data <- c(stats$Error[9],stats$Error[21])

# Bar Names Labels
names <- c("Protobuf", "JSON")

# Bar Axis Names

axis <- c("Data Format","Error %")

# Custom colors for the bars
bar_colors <- c("plum2", "cyan3")

# Create Bar
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))

# Add Value For Each Bar
text(x = graph, y = data, labels = data, pos = 3, col = "black")

# Graph Color Legend
legend("topright", legend = names, fill = bar_colors)
```

### Endpoint - GET Specific Plan

#### Elapsed Time
```{r}
# Graph Title

title <- "Stress GET Specific Plan Elapsed Time"

# Graph Data

data <- round(c(mTimePGSP, mTimeJGSP),2)

# Bar Names Labels
names <- c("Protobuf", "JSON")

# Bar Axis Names

axis <- c("Data Format","Elapsed Time (ms)")

# Custom colors for the bars
bar_colors <- c("plum2", "cyan3")

# Create Bar
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))

# Add Value For Each Bar
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")

# Graph Color Legend
legend("topright", legend = names, fill = bar_colors)
```

#### Bytes
```{r}
# Graph Title

title <- "Stress GET Specific Plan Bytes"

# Graph Data
data <- round(c(mBytesPGSP, mBytesJGSP), 2)

# Bar Names Labels
names <- c("Protobuf", "JSON")

# Bar Axis Names

axis <- c("Data Format","Bytes")

# Custom colors for the bars
bar_colors <- c("plum2", "cyan3")

# Create Bar
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))

# Add Value For Each Bar
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")

# Graph Color Legend
legend("topright", legend = names, fill = bar_colors)
```

#### Throughput
```{r}
title <- "Stress GET Specific Plan Throughput"

# Graph Data
data <- c(stats$Throughput[10],stats$Throughput[22])

# Bar Names Labels
names <- c("Protobuf", "JSON")

# Bar Axis Names

axis <- c("Data Format","Throughput /sec ")

# Custom colors for the bars
bar_colors <- c("plum2", "cyan3")

# Create Bar
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))

# Add Value For Each Bar
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")

# Graph Color Legend
legend("topright", legend = names, fill = bar_colors)

```

#### Error
```{r}
title <- "Stress GET Specific Plan Error"

# Graph Data
data <- c(stats$Error[10],stats$Error[22])

# Bar Names Labels
names <- c("Protobuf", "JSON")

# Bar Axis Names

axis <- c("Data Format","Error %")

# Custom colors for the bars
bar_colors <- c("plum2", "cyan3")

# Create Bar
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))

# Add Value For Each Bar
text(x = graph, y = data, labels = data, pos = 3, col = "black")

# Graph Color Legend
legend("topright", legend = names, fill = bar_colors)
```

### Endpoint - POST Subscriber

#### Elapsed Time
```{r}
# Graph Title

title <- "Stress POST Subscriber Elapsed Time"

# Graph Data

data <- round(c(mTimePPCS, mTimeJPCS),2)

# Bar Names Labels
names <- c("Protobuf", "JSON")

# Bar Axis Names

axis <- c("Data Format","Elapsed Time (ms)")

# Custom colors for the bars
bar_colors <- c("plum2", "cyan3")

# Create Bar
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))

# Add Value For Each Bar
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")

# Graph Color Legend
legend("topright", legend = names, fill = bar_colors)

```

#### Bytes
```{r}
title <- "Stress POST Subscriber Bytes"

# Graph Data
data <- round(c(mBytesPPCS, mBytesJPCS), 2)

# Bar Names Labels
names <- c("Protobuf", "JSON")

# Bar Axis Names

axis <- c("Data Format","Bytes")

# Custom colors for the bars
bar_colors <- c("plum2", "cyan3")

# Create Bar
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))

# Add Value For Each Bar
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")

# Graph Color Legend
legend("topright", legend = names, fill = bar_colors)
```

#### Throughput
```{r}
title <- "Stress POST Subscriber Throughput"

# Graph Data
data <- c(stats$Throughput[11],stats$Throughput[23])

# Bar Names Labels
names <- c("Protobuf", "JSON")

# Bar Axis Names

axis <- c("Data Format","Throughput /sec ")

# Custom colors for the bars
bar_colors <- c("plum2", "cyan3")

# Create Bar
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))

# Add Value For Each Bar
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")

# Graph Color Legend
legend("topright", legend = names, fill = bar_colors)
```

#### Error
```{r}
title <- "Stress POST Subscriber Error"

# Graph Data
data <- c(stats$Error[11],stats$Error[23])

# Bar Names Labels
names <- c("Protobuf", "JSON")

# Bar Axis Names

axis <- c("Data Format","Error %")

# Custom colors for the bars
bar_colors <- c("plum2", "cyan3")

# Create Bar
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))

# Add Value For Each Bar
text(x = graph, y = data, labels = data, pos = 3, col = "black")

# Graph Color Legend
legend("topright", legend = names, fill = bar_colors)

```

### Endpoint - POST Plan

#### Elapsed Time
```{r}
title <- "Stress POST Plan Elapsed Time"

# Graph Data

data <- round(c(mTimePPCP, mTimeJPCP),2)

# Bar Names Labels
names <- c("Protobuf", "JSON")

# Bar Axis Names

axis <- c("Data Format","Elapsed Time (ms)")

# Custom colors for the bars
bar_colors <- c("plum2", "cyan3")

# Create Bar
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))

# Add Value For Each Bar
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")

# Graph Color Legend
legend("topright", legend = names, fill = bar_colors)

```

#### Bytes
```{r}
title <- "Stress POST Plan Bytes"

# Graph Data
data <- round(c(mBytesPPCP, mBytesJPCP), 2)

# Bar Names Labels
names <- c("Protobuf", "JSON")

# Bar Axis Names

axis <- c("Data Format","Bytes")

# Custom colors for the bars
bar_colors <- c("plum2", "cyan3")

# Create Bar
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))

# Add Value For Each Bar
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")

# Graph Color Legend
legend("topright", legend = names, fill = bar_colors)
```

#### Throughput
```{r}
title <- "Stress POST Plan Throughput"

# Graph Data
data <- c(stats$Throughput[12],stats$Throughput[24])

# Bar Names Labels
names <- c("Protobuf", "JSON")

# Bar Axis Names

axis <- c("Data Format","Throughput /sec ")

# Custom colors for the bars
bar_colors <- c("plum2", "cyan3")

# Create Bar
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))

# Add Value For Each Bar
text(x = graph, y = data + 1, labels = data, pos = 3, col = "black")

# Graph Color Legend
legend("topright", legend = names, fill = bar_colors)
```

#### Error
```{r}
title <- "Stress POST Plan Error"

# Graph Data
data <- c(stats$Error[12],stats$Error[24])

# Bar Names Labels
names <- c("Protobuf", "JSON")

# Bar Axis Names

axis <- c("Data Format","Error %")

# Custom colors for the bars
bar_colors <- c("plum2", "cyan3")

# Create Bar
graph <- barplot(data, names.arg = names, xlab = axis[1], ylab = axis[2], col = bar_colors, main = title ,ylim = c(0, max(data) + max(data)/3))

# Add Value For Each Bar
text(x = graph, y = data, labels = data, pos = 3, col = "black")

# Graph Color Legend
legend("topright", legend = names, fill = bar_colors)

```

